% Product evaluation
% This chapter should describe the evaluation of the project.
% How did the project perform?
% Did it perform as expected/accomplish its goals?
% What issues arose during the project?

\subsection{Product evaluation}

Throughout the development of the project, the goals that were set out to be solved have, for the most part, been completed. The basis of a tool to restructure source code had successfully been created. The program also shows that being able to easily restructure a programs source would drastically reduce the time required to format documents to a users preferences compared to if it were to be done manually.

The performance of the tool runs fast enough within an integrated environment that it would not hinder the containing process or the development for the end user.
With various ways to run the program too, the user can choose how they would like to run the program and therefor this is less prone to vendor lock in.

By limiting the scope of the project to a single language, the project was able to be completed within the time frame set out. however, this has the downside of not being able to restructure code in other languages which is a particularly large limitation of this tool given that in recent years, web-based languages such as Typescript and Javascript as well as Python for AI based tasks, have become increasingly popular. By not making this tool multi-language compatible, it cannot be used to aid in enforcing coding standards to these other popular languages. If the project had a longer time frame and delivery period and with more resources available it would've been feasible to incorporate such a feature with more resources.
