% Identifying the problem
% Describe the problem that you are trying to solve, and why it is important.
% This will hopefully expand what you have looked for into what you have found
\subsection{Problem domain}

The object oriented programming paradigm has become one of the most popular programming paradigms in the industry \citep{6606742}. The wide adoptation of this paradigm has resulted in many large projects being written in an object oriented language.
Unfortunately, IT programs often fail to deliver intended results due to poor program management and governance \citep{7372958}. It becomes increasingly important to maintain high quality source code as it becomes harder to find bugs in later stages of development \citep{8681007} as well as potentially becoming too expensive and increasingly difficult to maintain \citep{8802820, 10.1145/2507288.2507312, 10.1145/3379597.3387457, 6606742, 7372958}, which then means programs can't be kept up-to-date which in turn could then introduce security vulnerabilities.
Developing healthy software is always a challenge \citep{8681007} and research indicates that there is a lack of standardization in the way software quality is measured \citep{6606742, 8681007}. This can make it difficult for developers to decide what methodologies to adopt \citep{6606742}. These issues all exist while there remains a high demand for high quality code \citep{6606742}.

Many of the papers in this area cover how important software quality is and the problems around the topic but only few provide approaches and solutions to solve the issues. For example, in the research conducted by \cite{6606742} they investigated a large number of papers that looked into software quality. Amongst those papers only 14.4\% of them went on to discuss the real world problems of software quality and of those papers only 2.7\% proposed solutions to solve the problem.

Further research into the area of software quality shows that teachers are struggling to teach students how to write high quality code \citep{10.1145/3428029.3428047}. This can have a knock on effect into the industry as students will be entering the industry with a lack of understanding of how to write high quality code, and so poorly written code may become more common despite the amount of research that is being conducted in the area of software quality.

It is clear, then, that there is a problem with software quality. While many papers have been written on the topic and the issues have been discussed, there is evidently a lack of real world solutions to the problem which is causing issues within the industry.
